---
title: "Résumé"
description: |
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{css All, echo=FALSE}
a {n  
  text-decoration: none; 
  color: rgba(121, 205, 205);
}
a:hover {
  color: rgba(255, 182, 255, 0.8);
}
ul {
  list-style: none; /* Remove list bullets bcz don't know how to change color */
  padding: 0;
  margin: 0;
}
li::before {
  content: "•"; 
  color: "#5A59A3";
}
h1 {
  font-family: candara; /* title */
  font-style: italic;
}
h2 {
  font-family: candara;
  font-style: italic;
  color: rgba(134, 35, 141, 0.72);
}
p code,
li code {
    line-height: 2.0; 
    white-space: nowrap;
}
body {
    width: 100vw;
    height: 100vh;
    margin: 0;
    background: linear-gradient(
        130deg, 
        #5A59A3, 
        #C66060
    ) no-repeat  fixed;
}
```

## Education
Master in Taxation: Adkerson School of Accountancy [Expected Graduattion Date]{style="float:right"}  
  
Bachelor of Business in Accounting: Adkerson School of Accountancy [May 2020]{style="float:right"}    
Minor in Business Analytics  
Mississippi State University, Mississippi State, MS

## Working Experience
- &nbsp;&nbsp;Private Accountant for a Fire Protection Service Company[Fall 2014 – Fall 2015]{style="float: right"}  
- &nbsp;&nbsp;Hunan, China  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;Journal entries and general ledger preparation  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;Bank statements and reconciliation  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;Examining expenses submitted by the construction manager  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;Taxation preparation during tax season

## Course Group Projects
-	&nbsp;&nbsp;PowerPoint and social platforms: Marketing strategy plans for a drone startup
- &nbsp;&nbsp;Excel and Word: Prepared consolidated financial reports for company acquisition
- &nbsp;&nbsp;R: Bankruptcy analysis. Methods: holdout validation in discriminant analysis and logistic &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; regression analysis, and cross-validation in decision tree analysis

## Computer Skills
- &nbsp;&nbsp;Advanced in Microsoft Office including Excel, Word, and PowerPoint
- &nbsp;&nbsp;Developing knowledge in Access, R, SAS, and Tableau

## Volunteer Work
- &nbsp;&nbsp;West Point Clay County Animal Shelter 
- &nbsp;&nbsp;MSU Community Garden 
- &nbsp;&nbsp;Starkville Community Farmers Market 
- &nbsp;&nbsp;The Salvation Army

```{r include=FALSE}
# https://github.com/yixuan/prettydoc/blob/master/inst/resources/css/hpstr.css
# https://www.w3schools.com/cssref/tryit.asp?filename=trycss_content_list-bullets
# https://rstudio4edu.github.io/rstudio4edu-book/doc-fancy.html
# https://www.sololearn.com/Discuss/1780258/how-do-i-remove-the-weird-lines-on-the-linear-gradient
```

